Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-08 Methods.tex
MOAR TABLES!

\begin{table}
\center
\begin{tabular} {l | c}
Name & Value \\

\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
 \cite{Bijak2013b}

@@

\begin{table}
\center
\begin{tabular} {l | c}
Name & Value \\

\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

\begin{table}
\center
\begin{tabular} {l | c}
Name & Value \\

>>>>

\begin{table}
\center
\begin{tabular} {|l | c | r|}
\hline
Name & Description & Value \\ \hline
\(N_{w}\) & Number of women & 1000 \\ \hline
\(N_{m}\) & Number of midwives & 100 \\ \hline
k & Number of appointments per midwive & 1000 \\ \hline
A & Maximum number of appointments per woman & 12 \\ \hline
R & Runs & 1000 \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(p_{w}\) & Probability of women sharing & 0. \\ \hline
\(q_{w}\) & Weight of shared information for women & 0. \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 10 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
 \cite{Bijak2013b}

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(p_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(q_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(Payoff_{baby}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(Payoff_{referral}\) & Cost for referral & \multicolumn{2}{l|}{\(Payoff_{baby} - 1\)} \\ \hline
\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 1 & 100 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

\begin{table}
\center
\begin{tabular} {| l | l |}
Name & Description \\ \hline
